---
title: "p8105_hw5_yc4016"
output: github_document
date: "2022-11-08"
author: "Yishan Chen"
---

```{r setup, include=FALSE}
library(tidyverse)
library(readr)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


# Problem 1

### Question
* Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:
  * Start with a dataframe containing all file names; the list.files function will help
  * Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
  * Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
* Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.




# Problem 2

```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  mutate(city_state = str_c(city, state, sep = ", ", collapse = NULL),
         solved_homicide = case_when(disposition == "Closed without arrest" ~ "unsolved",
                                      disposition == "Open/No arrest"        ~ "unsolved",
                                      disposition == "Closed by arrest"      ~ "solved"))
```











