---
title: "p8105_hw5_yc4016"
output: github_document
date: "2022-11-08"
author: "Yishan Chen"
---

```{r setup, include=FALSE}
library(tidyverse)
library(readr)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


# Problem 1

### Question
* Create a tidy dataframe containing data from all participants, including the subject ID, arm, and observations over time:
  * Start with a dataframe containing all file names; the list.files function will help
  * Iterate over file names and read in data for each subject using purrr::map and saving the result as a new variable in the dataframe
  * Tidy the result; manipulate file names to include control arm and subject ID, make sure weekly observations are “tidy”, and do any other tidying that’s necessary
* Make a spaghetti plot showing observations on each subject over time, and comment on differences between groups.




# Problem 2

```{r}
homicide_df = 
  read_csv("./data/homicide-data.csv") %>% 
  mutate(city_state = str_c(city, state, sep = ", ", collapse = NULL),
         homicide_situation = case_when(disposition == "Closed without arrest" ~ "unsolved",
                                        disposition == "Open/No arrest"        ~ "unsolved",
                                        disposition == "Closed by arrest"      ~ "solved")) %>% 
  select(city_state, homicide_situation, everything()) 

homicide_df
```

##### Find total number of homicides by cities and total number of unsolved homicides by cities. 
```{r}
homicide_number = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(total_homicide = n(),
            total_homicide_unsolved = sum(homicide_situation == "unsolved"))

homicide_number
```

#### Estimate the proportion of homicides that are unsolved for baltimore.
```{r}
baltimore = 
  homicide_number %>% 
  filter(city_state == "Baltimore, MD")

baltimore

prop.test(baltimore %>% pull(total_homicide_unsolved), 
          baltimore %>% pull(total_homicide)) %>% 
broom::tidy() 
```

#### Estimate the proportion of unsolved homicides and the confidence interval for each of the cities.
```{r}
each_cities = 
  homicide_number %>% 
  mutate(prop_cities = map2(.x = total_homicide_unsolved, .y = total_homicide, ~prop.test(x = .x, n = .y)),
         tidy_cities = map(.x = prop_cities, ~ broom::tidy(.x))) %>% 
  unnest(tidy_cities) %>% 
  select(-prop_cities, city_state, estimate, conf.low, conf.high) %>% 
  janitor::clean_names() 

each_cities
```

#### Create a plot that shows the estimates and CIs for each city
```{r}
plot_each_cities =
  each_cities %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  geom_errorbar(aes(ymin = conf_low, ymax = conf_high)) +
  labs(title = "Estimates and confidence intervals of unsolved homocide for each city",x = "cities") 
plot_each_cities
```


# Problem 3

```{r}
norm_mean_p = function(n=30, mu, sigma = 5) {
  norm_data = tibble(x = rnorm(n, mean = mu, sd = sigma))
  norm_data %>% 
    t.test (mu = 0, alpha = 0.05, conf.level = 0.95) %>% 
     broom::tidy ()
}

norm_mean_p
```

```{r}
norm_results = 
  expand_grid(mu = c(0,1,2,3,4,5,6),
              iteration = 1:100) %>% 
  mutate(estimate_df = map(mu, ~norm_mean_p(mu=.x))) %>% 
  unnest(estimate_df)

norm_results
```

#### Plot showing the proportion of times the null was rejected and the true value of mu.
```{r}
plot1 = 
  norm_results%>%
    group_by(mu) %>%
    summarize(n_sum = n(),
              p_value_sum = sum(p.value < 0.05)) %>% 
    mutate (proportion_rejected = p_value_sum / n_sum) %>% 
  ggplot(aes(x = mu, y = proportion_rejected)) + 
  geom_point() + 
  labs(title = " The proportion of times the null was rejected and the true value of mu", 
       x = "The true value of means",
       y = "The proportion of times the null was rejected") 

plot1
```

#### Plot showing the average estimate of mu_hat and the true value of mu.
```{r}
plot2 = 
  norm_results %>%
    group_by(mu) %>%
    summarize(ave_estimate_mu_hat = mean(estimate)) %>%
    ggplot(aes(x = mu, y = ave_estimate_mu_hat, group = mu)) + 
    geom_point() +
    labs(title = "The average estimate of mu_hat and the true value of mu", 
         x = "The true value of mu", 
         y = "The average estimate of mu_hat") 
plot2
```

#### Plot showing the average estimate of mu_hat only in samples for which the null was rejectedand the true value of mu.
```{r}
plot3 = 
  norm_results %>%
    group_by(mu) %>%
    filter(p.value < 0.05) %>% 
    summarize(ave_estimate_mu_hat = mean(estimate)) %>%
    ggplot(aes(x = mu, y = ave_estimate_mu_hat, group = mu)) + 
    geom_point() + 
    labs(title = "The average estimate of mu_hat and the true value of mu", 
         x = "The true value of mu", 
         y = "The average estimate of mu_hat only in samples for which the null was rejected") 
plot3
```


